\section{Coalition: who is behind it, and is the opposition manageable?}
\label{sec:coalition}

The seventh question is about the room outside the chamber. A member counts who will
testify for the bill, who will score it, and who, if anyone, will organize against
it, because a bill with a broad coalition and no determined opponent is a bill a whip
can move.

The coalition for H. R. 9510 assembles from groups that rarely align. Oncology and
patient-safety organizations have a clear interest in a mandatory safety floor before
an autonomous robot acts. Patient advocates and rural-access coalitions benefit from
the platform's reach into underserved districts. Device and robotics manufacturers
and the standards bodies gain predictable rules of the road, because the gates are
bound to the consensus standards those bodies already publish \cite{asme2018vv40,
isots15066, ul4600}. The States keep their human-over-AI laws through the savings
clause. The author's prior analysis of how proposed bills rank by patient priority
places verification before generation at the top of the list a patient would choose
\cite{Kawchak2026PatientPriorityProposedU}. \autoref{fig:coalition} shows the
coalition radiating from the bill.

\begin{psgfig}
\node[psgact] (c) at (0,0) {Support for\\H. R. 9510};
\node[psgone] (a) at (4.4,1.6) {Clinicians and\\safety groups};
\node[psgtwo] (b) at (4.4,0.0) {Patients and\\rural access};
\node[psgthree] (d) at (4.4,-1.6) {Industry and\\standards bodies};
\draw[psgedge] (c) to[out=55,in=180,looseness=0.6] (a.west);
\draw[psgedge] (c)--(b.west);
\draw[psgedge] (c) to[out=-55,in=180,looseness=0.6] (d.west);
\end{psgfig}
\psgcaption{\textbf{Figure 8.} The supporting coalition radiates from the bill into
clinicians, patients, and industry; the colored TikZ reproduction of catalog diagram
13. Each curved arrow carries an explicit looseness of 0.6.}

The opposition is manageable because the bill gives little to organize against. It
creates no entitlement to cut, imposes no new tax or fee, preempts little, and binds
its rigor to standards the industry helped write. The predictable objections, that it
costs too much, that it is federal overreach, that it will chill innovation, or that
it is redundant, each have a specific answer in the text: the clean score, the
savings clause, the change-control carve-outs, and the fact that the closest
analogues remain voluntary. Routing each objection to its cited answer, rather than
avoiding it, is what keeps a coalition together through markup.

Coalition is answered by breadth and the absence of a natural enemy: many groups gain,
few lose, and every standard objection has a citation waiting.
