% Back matter adapted from review/final-narrative/sections/back_matter.tex:
% Acknowledgments, Ethical Disclosures, Rights and Permissions, Cite This
% Framework, Data Availability. Each is added to the table of contents.

\bmhead{Acknowledgments}
The author acknowledges Anthropic for access to Claude Code for the instruction,
drafting, and assembly of this framework; OpenAI for ChatGPT subject support; and
Google Gemini for additional research assistance.

\bmhead{Ethical Disclosures}
The author declares no competing interests. This is an independent framework and is
not endorsed, sponsored, or approved by any trial sponsor, CRO, site, IRB,
regulator, or medical society, nor by CFR, ICH, or FDA. H. R. 9510 is an
illustrative bill number; it is not enacted law and this framework is not legal or
clinical advice. All supporting numbers are simulation or illustrative results
unless tied to a cited source.

\bmhead{Rights and Permissions}
This framework is distributed under the Creative Commons Attribution 4.0
International License (CC BY 4.0). To view a copy, visit
\url{https://creativecommons.org/licenses/by/4.0/}. Reproduced public-domain U.S.
Government text is used under 17 U.S.C. \S~105.

\bmhead{Cite This Framework}
Kawchak K. Earning the Clinician's Trust: An Eight-Question Confidence Framework
for Verified Physical AI in Oncology Trials. Zenodo. 2026;
\href{https://doi.org/10.5281/zenodo.xxxxxxxx}{10.5281/zenodo.xxxxxxxx}.

\bmhead{Data Availability}
All sources, figures, and prompt records supporting this framework are openly
available in the \texttt{kevinkawchak/law-physical-ai-trials} repository under
\texttt{adoption/} (the prompt, the four sub-prompts, the colored Mermaid catalog,
and the three framework stages), and build on the prior review under
\texttt{review/} and the author's Zenodo deposits. All data sets are synthetic or
illustrative; no patient-identifiable information is included.
