\section{Constituents: who does this help back home?}
\label{sec:constituents}

The fifth question is local. A member votes for what helps the district and the
State, and a national platform that reaches every region gives every member a
concrete reason to be for the bill.

The platform that H. R. 9510 governs is designed to scale across the country. Its
implementation strategy moves from a single site, to five through ten multi-state
sites, to a steady state of 50 through 100 operational sites spanning all major
geographic regions, with rolling activation of new sites each quarter
\cite{Kawchak2026NationalPlatformPhysicalAI, Kawchak2026PhysicalAIOncologyClinical}.
For a constituent, that scale translates into faster enrollment through automated
screening, lower per-patient cost as fixed infrastructure is amortized over more
patients, and access to advanced oncology trials closer to home, including in rural
and underserved areas that rarely host a trial today. The convergence of human and
machine performance that makes this possible is the same one documented across
high-performance medicine \cite{topol2019high}. \autoref{fig:reach} shows the
rollout, and \autoref{tab:constituents} lists what each phase delivers to a district.

\begin{psgfig}
\node[psgone] (p1) at (0,0) {Phase 1\\1 site};
\node[psgevid] (p2) at (4.0,0) {Phase 2\\5 to 10 sites};
\node[psgact] (p3) at (8.0,0) {Phase 3\\50 to 100 sites};
\node[psgtwo] (r) at (4.0,-2.0) {Rural and\\underserved reach};
\draw[psgedge] (p1)--(p2); \draw[psgedge] (p2)--(p3);
\draw[psgedge] (p3) to[out=-120,in=0,looseness=0.7] (r.east);
\end{psgfig}
\psgcaption{\textbf{Figure 6.} The national rollout from one site to a steady state of
50 through 100, reaching rural and underserved districts; the colored TikZ
reproduction of catalog diagram 11.}

\needspace{10\baselineskip}\begin{table}[H]
\footnotesize
\begin{tabularx}{\textwidth}{@{}L{3.0cm} Y@{}}
\toprule
\textbf{What the district gets} & \textbf{How the platform delivers it}\\
\midrule
Faster trial access & Automated screening and eligibility checks compress the time from referral to enrollment.\\
Lower patient cost & Fixed infrastructure is amortized across more patients, so per-patient cost falls as volume rises.\\
Rural and underserved reach & Multi-site deployment targets all major regions rather than a few coastal centers.\\
New skilled jobs & Site operation creates roles in Physical AI operation, robot maintenance, and AI safety monitoring.\\
\bottomrule
\end{tabularx}
\caption{Constituent benefit by phase: what the platform the bill enables delivers to
a member's district and State.}
\label{tab:constituents}
\end{table}

Constituents are answered with reach: a platform that, once the bill makes its safety
floor law, can bring advanced oncology trials and skilled work to districts that have
never had either.
