\section{Appendix A: figure compendium}
\label{sec:appendix-figures}

This appendix reproduces the remaining figures from the Mermaid catalog
(\texttt{enactment/mermaid/}) as colored TikZ, so the framework carries the full set
of twenty exhibits in the strict palette (black, grayscales, \#4B0082, \#000080,
\#C0C0C0). Every figure keeps a uniform \texttt{\textbackslash vspace\{-0.75cm\}}
between the figure and its caption.

\begin{psgfig}
\node[psgone] (b) at (0,0) {Bill on\\the desk};
\node[psgdec] (q) at (3.9,0) {Eight\\questions};
\node[psgevid] (y) at (7.6,1.2) {Cosponsor};
\node[psgthree] (a) at (7.6,0) {Amend};
\node[psgcaut] (n) at (7.6,-1.2) {Decline};
\draw[psgedge] (b)--(q);
\draw[psgedge] (q)--(y.south west);
\draw[psgedge] (q)--(a.west);
\draw[psgedge] (q)--(n.north west);
\draw[psgedged] (a) to[out=180,in=-10,looseness=0.5] (q.south east);
\end{psgfig}
\psgcaption{\textbf{Figure 10.} The passage decision: the eight questions gate one
choice with three guarded outcomes, and an amendment adopted at markup returns to the
questions (diagram 01).}

\begin{psgfig}
\node[psgone] (g1) at (0,0.9) {Gates 1 to 5\\and 7, 8};
\node[psgact] (g2) at (0,-0.9) {Hard predicates\\6, 9, 10};
\node[psgdec] (d) at (4.2,0) {Fraction\\= 1.0?};
\node[psgevid] (c) at (8.2,0.9) {Cleared to\\generate};
\node[psgcaut] (b) at (8.2,-0.9) {BLOCK};
\draw[psgedge] (g1) to[out=0,in=120,looseness=0.7] (d.north west);
\draw[psgedge] (g2) to[out=0,in=-120,looseness=0.7] (d.south west);
\draw[psgedge] (d)--(c.south west); \draw[psgedge] (d)--(b.north west);
\end{psgfig}
\psgcaption{\textbf{Figure 11.} The ten gates Congress is enacting: the routine gates
and the three hard catastrophe predicates both feed the verification-fraction test
(diagram 04).}

\begin{psgfig}
\node[psgact] (c) at (0,0) {Section 515D\\360e-5};
\node[psgone] (a) at (4.4,1.4) {Scope: 321(h),\\331, 351};
\node[psgtwo] (p) at (4.4,0.0) {Pathways: 355g,\\360(k), 360c, 360e};
\node[psgthree] (b) at (4.4,-1.4) {Boundaries: 360j(o),\\360k savings};
\draw[psgedge] (c) to[out=50,in=180,looseness=0.6] (a.west);
\draw[psgedge] (c)--(p.west);
\draw[psgedge] (c) to[out=-50,in=180,looseness=0.6] (b.west);
\end{psgfig}
\psgcaption{\textbf{Figure 12.} The amendment map: one new section radiates ten
conforming amendments into Title 21 (diagram 05).}

\begin{psgfig}
\node[psgone] (i) at (0,0) {Introduce\\and refer};
\node[psgtwo] (m) at (3.6,0) {Markup};
\node[psgact] (h) at (7.2,0) {House\\passage};
\node[psgevid] (s) at (10.8,0) {Senate\\passage};
\draw[psgedge] (i)--(m); \draw[psgedge] (m)--(h); \draw[psgedge] (h)--(s);
\end{psgfig}
\psgcaption{\textbf{Figure 13.} The legislative journey from introduction through
House and Senate passage (diagram 06).}

\begin{psgfig}
\node[psgone] (s1) at (0,1.1) {ASME V\&V 40};
\node[psgone] (s2) at (0,0) {ISO 14971};
\node[psgone] (s3) at (0,-1.1) {IEC 80601-2-77};
\node[psgact] (e) at (4.4,0) {Ten-gate\\examination};
\node[psgevid] (o) at (8.6,0) {ACCEPT,\\ESCALATE, BLOCK};
\draw[psgedge] (s1) to[out=0,in=150,looseness=0.6] (e.north west);
\draw[psgedge] (s2)--(e.west);
\draw[psgedge] (s3) to[out=0,in=-150,looseness=0.6] (e.south west);
\draw[psgedge] (e)--(o);
\end{psgfig}
\psgcaption{\textbf{Figure 14.} The recognized standards basis: consensus standards
flow into the one examination the statute requires (diagram 10).}

\begin{psgfig}
\node[psgone] (s) at (0,0) {24-hour sim\\168 patients};
\node[psgevid] (u) at (4.2,0) {99.7\% uptime\\zero harm};
\node[psgact] (c) at (8.4,0) {Bill codifies a\\demonstrated system};
\draw[psgedge] (s)--(u); \draw[psgedge] (u)--(c);
\end{psgfig}
\psgcaption{\textbf{Figure 15.} The platform as proof of implementability: validated
simulation evidence supports codification (diagram 14).}

\begin{psgfig}
\node[psgact] (h) at (0,0) {House passes};
\node[psgevid] (s) at (3.7,0) {Senate companion\\passes};
\node[psgtwo] (r) at (7.4,0) {Reconcile};
\node[psgact] (l) at (11.1,0) {Sign};
\draw[psgedge] (h)--(s); \draw[psgedge] (s)--(r); \draw[psgedge] (r)--(l);
\draw[psgedged] (s) to[out=-120,in=-60,looseness=0.5] (h.south);
\end{psgfig}
\psgcaption{\textbf{Figure 16.} The two-chamber strategy: a Senate companion runs in
parallel and the versions are reconciled before signature (diagram 15).}

\begin{psgfig}
\node[psgone] (i) at (0,0) {Introduced};
\node[psgtwo] (c) at (3.4,-1.0) {Committee print\\and amendment};
\node[psgact] (r) at (6.8,0) {Reported};
\node[psgevid] (p) at (10.2,0) {Passed};
\draw[psgedge] (i)--(r);
\draw[psgedge] (i) to[out=-90,in=180,looseness=0.6] (c.west);
\draw[psgedge] (c) to[out=0,in=-90,looseness=0.6] (r.south);
\draw[psgedge] (r)--(p);
\end{psgfig}
\psgcaption{\textbf{Figure 17.} The markup lifecycle as a branch and merge of the
text: a committee branch refines the bill before it merges back as reported
(diagram 16).}

\begin{psgfig}
\node[psgact] (h) at (0,0) {House\\218 of 435};
\node[psgevid] (c) at (4.0,0) {Senate cloture\\60};
\node[psgact] (s) at (8.0,0) {Senate passage\\51 of 100};
\draw[psgedge] (h)--(c); \draw[psgedge] (c)--(s);
\end{psgfig}
\psgcaption{\textbf{Figure 18.} The vote thresholds passage must satisfy in each
chamber (diagram 17).}

\begin{psgfig}
\node[psgdec] (o) at (0,0) {Stated\\objection};
\node[psgevid] (a) at (4.6,2.1) {Cost: zero net,\\19 to 1 saving};
\node[psgevid] (b) at (4.6,0.7) {Overreach: savings\\clause};
\node[psgevid] (c) at (4.6,-0.7) {Chill: 510(k)\\carve-outs};
\node[psgcaut] (d) at (4.6,-2.1) {Other: route to\\amendment};
\draw[psgedge] (o)--(a.west); \draw[psgedge] (o)--(b.west);
\draw[psgedge] (o)--(c.west); \draw[psgedge] (o)--(d.west);
\end{psgfig}
\psgcaption{\textbf{Figure 19.} Handling the standard objections: each predictable
objection routes to a cited answer, and only a new concern routes to an amendment
(diagram 18).}

\begin{psgfig}
\node[psgone] (s) at (0,0) {Scored};
\node[psgtwo] (z) at (3.6,0) {Zero net\\mandatory};
\node[psgevid] (c) at (7.2,0) {CutGo\\compatible};
\node[psgact] (f) at (10.8,0) {Cleared for\\the floor};
\draw[psgedge] (s)--(z); \draw[psgedge] (z)--(c); \draw[psgedge] (c)--(f);
\end{psgfig}
\psgcaption{\textbf{Figure 20.} The scoring path: a discretionary authorization clears
the budget points of order and reaches the floor (diagram 19).}

\vspace{0.2cm}
Taken together, the twenty figures trace one claim from a single member's reading of
the bill (Figure 10) to enactment in both chambers and a platform ready to implement
it (Figure 9). None asks a member to vote on faith; each shows where a gate, a score
line, a provision, or a coalition makes the yes defensible.
