
\clearpage
\bmhead{Acknowledgments}
The author thanks the open standards and patient-safety communities whose published
work the verification floor rests on. The author also thanks Claude Code Opus 4.8 Max for paper generation from the author's prompt, which was further then edited by the author. Additionally, the author appreciates ChatGPT 5.5 Instant, ChatGPT 5.5 Thinking Extended, Gemini 3.5 Flash, and Gemini 3.1 Pro for troubleshooting and manuscript code fixes. 

\bmhead{Ethical disclosures}
The author declares no competing interests. This is independent research. It is not endorsed or sponsored by the Congress, the
FDA, HHS, any Member or committee, any trial sponsor, contract research
organization, institutional review board, or medical society. It is not enacted law
and not legal advice. The number ``H. R. 9510'' 2026 is illustrative. All supporting numbers are simulation or illustrative results unless tied to a source.


\bmhead{Rights and permissions}
This framework is distributed under the Creative Commons Attribution 4.0
International License (CC BY 4.0). To view a copy, visit
\url{https://creativecommons.org/licenses/by/4.0/}. Reproduced public-domain U.S.
Government text is used under 17 U.S.C. \S~105. 

\bmhead{Cite this article}
Kawchak, K. (2026). Earning the Congress's Vote: A New Oncology Trial Framework for Enacting H. R. 9510. Zenodo. \href{https://doi.org/10.5281/zenodo.20726461}{10.5281/zenodo.20726461}.

\bmhead{Data availability}
All source files, the figure catalog, and the references are available in the enactment/ directory of the kevinkawchak/law-physical-ai-trials
repository, and the author's Zenodo deposits.\ No proprietary data is used; all supporting numbers are illustrative or
simulation results unless tied to a cited source. All data sets are synthetic or illustrative; no patient-identifiable information is included. A rundown of AI and user edit times in useredits.md are available at enactment/final-framework/publication (4.97 hours).

  
